An assessment of photometric redshift PDF performance in the context of LSST

### 2018-09-04 paper/tex/results.tex
add/modify text describing Fig 4 update
add clarification on overtraining

\begin{table}
\setlength{\tabcolsep}{2pt}
\centering
\caption{The fraction of ``catastrophic outlier'' PIT values.  We expect a value of 0.0002 for a proper Uniform distribution.  An excess over this small value indicates true redshifts that fall outside the non-zero support of the $p(z)$.  }\label{tab:pitoutlier}
\begin{tabular}{lc}
\hline
\hline
 ``catastrophic outlier''\\ PIT fraction\\
\hline
Photo-z Code & fraction PIT$<10^{-4}$ or $>$0.9999\\
\hline
\textsc{ANNz2} & 0.0265\\
\textsc{BPZ} & 0.0192\\
\textsc{Delight} & 0.0006\\
\textsc{EAZY} & 0.0154\\
\textsc{FlexZBoost} & 0.0202\\
\textsc{GPz} & 0.0058\\
\textsc{LePhare} & 0.0486\\
\textsc{METAPhoR}& 0.0229\\
\textsc{CMNN} & 0.0034\\
\textsc{Skynet} & 0.0001\\
\textsc{TPZ} & 0.0130\\
\hline
\textsc{TrainZ} & 0.0002\\
\end{tabular}
\end{table}

@@

Two of the machine learning based codes, \textsc{ANNz2} and \textsc{METAPhoR}, appear to be over-trained, adding excess galaxy probability to the redshift peaks and missing probability in the troughs.

@@

\begin{table}  %%% DATA TABLE %%%
\centering
\caption{CDE loss statistic for each photo-$z$ code.} \label{tab:cdeloss}
\begin{tabular}{lr}
\hline
\bf Photo-$z$ Code & \bf CDE Loss \\
\hline
\textsc{ANNz2} 		& $-6.88$ \\
\textsc{BPZ} 		& $-7.82$ \\
%\textsc{Delight} 	& $-4.06$ \\
\textsc{Delight}    & $-8.33$\\
%\textsc{EAZY} 		& $-7.97$ \\
\textsc{EAZY}       & $-7.07$ \\
%\textsc{FlexZBoost} & $-11.51$ \\
\textsc{FlexZBoost} & $-10.60$\\
\textsc{GPz} 		& $-9.93$ \\
\textsc{LePhare} 	& $-1.66$ \\
\textsc{METAPhoR} 	& $-6.28$ \\
%\textsc{CMNN} 		& $-$ \\
\textsc{CMNN}         & $-10.43$ \\
\textsc{SkyNet} 	& $-7.89$ \\
\textsc{TPZ} 		& $-9.55$ \\
\hline
\trainz		& $-0.83$ \\
%\textsc{Frankenz}	& $-$  \\
%\hline
\end{tabular}
\end{table}

\begin{table}
\setlength{\tabcolsep}{2pt}
\begin{center}
\caption{Root-Mean-Square-Error (RMSE) statistics for the twelve photo-z codes for both PIT and $\hat{N}(z)$ distributions.}\label{tab:rmse}
\begin{tabular}{lcc}
\hline
\hline
Root-Mean-Square-Error \\
(RMSE) statistics \\
\hline
Photo-z Code & PIT RMSE & N(z) RMSE\\
\hline
\textsc{ANNz2}      & 0.019 & 0.0054\\
\textsc{BPZ}        & 0.032 & 0.0050\\
\textsc{Delight}    & 0.111 & 0.0056\\
\textsc{EAZY}       & 0.054 & 0.0102\\
\textsc{FlexZBoost} & 0.021 & 0.0022\\
\textsc{GPz}        & 0.027 & 0.0042\\
\textsc{LePhare}    & 0.028 & 0.0062\\
\textsc{METAPhoR}   & 0.064 & 0.0081\\
\textsc{CMNN}         & 0.108 & 0.0009\\
\textsc{Skynet}     & 0.054 & 0.0144\\
\textsc{TPZ}        & 0.082 & 0.0031\\
\hline
\trainz		& 0.0025 & 0.0013\\
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\caption{Moments of the stacked $\hat{N}(z)$ distribution}\label{tab:moments}
\begin{tabular}{lccc}
\hline
\hline
 \multicolumn{4}{l}{Stacked $n(z)$ Moments} \\
\hline
              & 1st Moment & 2nd Moment & 3rd Moment \\
\textsc{Truth}     & 0.701      &   0.630    & 0.671  \\
\hline
Photo-z Code       & 1st Moment & 2nd Moment & 3rd Moment\\
\hline
\textsc{ANNz2}     & 0.702      & 0.625      & 0.653    \\
\textsc{BPZ}       & 0.699      & 0.629      & 0.671    \\
\textsc{Delight}   & 0.692      & 0.609      & 0.638    \\
\textsc{EAZY}      & 0.681      & 0.595      & 0.619    \\
\textsc{FlexZBoost}& 0.694      & 0.610      & 0.631    \\
\textsc{GPz}       & 0.696      & 0.615      & 0.639    \\
\textsc{LePhare}   & 0.718      & 0.668      & 0.741    \\
\textsc{METAPhoR}  & 0.705      & 0.628      & 0.657    \\
\textsc{CMNN}        & 0.701      & 0.628      & 0.667    \\
\textsc{Skynet}    & 0.743      & 0.708      & 0.797    \\
\textsc{TPZ}       & 0.700      & 0.619      & 0.643    \\
\hline
\trainz	   & 0.699 		& 0.627 	& 0.666 \\
\end{tabular}
\end{table}

>>>>

\begin{table}
\setlength{\tabcolsep}{2pt}
\centering
\caption{The fraction of ``catastrophic outlier'' PIT values.  We expect a value of 0.0002 for a proper Uniform distribution.  An excess over this small value indicates true redshifts that fall outside the non-zero support of the $p(z)$.  }\label{tab:pitoutlier}
\begin{tabular}{lc}
\hline
\hline
 ``catastrophic outlier''\\ PIT fraction\\
\hline
Photo-z Code & fraction PIT$<10^{-4}$ or $>$0.9999\\
\hline
\textsc{ANNz2} & 0.0265\\
\textsc{BPZ} & 0.0192\\
\textsc{Delight} & 0.0006\\
\textsc{EAZY} & 0.0154\\
\textsc{FlexZBoost} & 0.0202\\
\textsc{GPz} & 0.0068\\
\textsc{LePhare} & 0.0486\\
\textsc{METAPhoR}& 0.0229\\
\textsc{CMNN} & 0.0034\\
\textsc{Skynet} & 0.0001\\
\textsc{TPZ} & 0.0130\\
\hline
\textsc{TrainZ} & 0.0002\\
\end{tabular}
\end{table}

@@

Two of the machine learning based codes, \textsc{ANNz2} and \textsc{METAPhoR}, appear to be over-trained, adding excess galaxy probability to the redshift peaks with the largest number of training galaxies, and missing probability in the troughs where training galaxies are of fewer number.

@@

\begin{table}  %%% DATA TABLE %%%
\centering
\caption{CDE loss statistic for each photo-$z$ code.} \label{tab:cdeloss}
\begin{tabular}{lr}
\hline
\bf Photo-$z$ Code & \bf CDE Loss \\
\hline
\textsc{ANNz2} 		& $-6.88$ \\
\textsc{BPZ} 		& $-7.82$ \\
%\textsc{Delight} 	& $-4.06$ \\
\textsc{Delight}    & $-8.33$\\
%\textsc{EAZY} 		& $-7.97$ \\
\textsc{EAZY}       & $-7.07$ \\
%\textsc{FlexZBoost} & $-11.51$ \\
\textsc{FlexZBoost} & $-10.60$\\
\textsc{GPz} 		& $-9.56$ \\
\textsc{LePhare} 	& $-1.66$ \\
\textsc{METAPhoR} 	& $-6.28$ \\
%\textsc{CMNN} 		& $-$ \\
\textsc{CMNN}         & $-10.43$ \\
\textsc{SkyNet} 	& $-7.89$ \\
\textsc{TPZ} 		& $-9.55$ \\
\hline
\trainz		& $-0.83$ \\
%\textsc{Frankenz}	& $-$  \\
%\hline
\end{tabular}
\end{table}

\begin{table}
\setlength{\tabcolsep}{2pt}
\begin{center}
\caption{Root-Mean-Square-Error (RMSE) statistics for the twelve photo-z codes for both PIT and $\hat{N}(z)$ distributions.}\label{tab:rmse}
\begin{tabular}{lcc}
\hline
\hline
Root-Mean-Square-Error \\
(RMSE) statistics \\
\hline
Photo-z Code & PIT RMSE & N(z) RMSE\\
\hline
\textsc{ANNz2}      & 0.019 & 0.0054\\
\textsc{BPZ}        & 0.032 & 0.0050\\
\textsc{Delight}    & 0.111 & 0.0056\\
\textsc{EAZY}       & 0.054 & 0.0102\\
\textsc{FlexZBoost} & 0.021 & 0.0022\\
\textsc{GPz}        & 0.048 & 0.0042\\
\textsc{LePhare}    & 0.028 & 0.0062\\
\textsc{METAPhoR}   & 0.064 & 0.0081\\
\textsc{CMNN}         & 0.108 & 0.0009\\
\textsc{Skynet}     & 0.054 & 0.0144\\
\textsc{TPZ}        & 0.082 & 0.0031\\
\hline
\trainz		& 0.0025 & 0.0013\\
\end{tabular}
\end{center}
\end{table}

@@

\begin{table}
\setlength{\tabcolsep}{2pt}
\caption{Moments of the stacked $\hat{N}(z)$ distribution}\label{tab:moments}
\begin{tabular}{lccc}
\hline
\hline
 \multicolumn{4}{l}{Stacked $n(z)$ Moments} \\
\hline
              & 1st Moment & 2nd Moment & 3rd Moment \\
\textsc{Truth}     & 0.701      &   0.630    & 0.671  \\
\hline
Photo-z Code       & 1st Moment & 2nd Moment & 3rd Moment\\
\hline
\textsc{ANNz2}     & 0.702      & 0.625      & 0.653    \\
\textsc{BPZ}       & 0.699      & 0.629      & 0.671    \\
\textsc{Delight}   & 0.692      & 0.609      & 0.638    \\
\textsc{EAZY}      & 0.681      & 0.595      & 0.619    \\
\textsc{FlexZBoost}& 0.694      & 0.610      & 0.631    \\
\textsc{GPz}       & 0.692      & 0.605      & 0.619    \\
\textsc{LePhare}   & 0.718      & 0.668      & 0.741    \\
\textsc{METAPhoR}  & 0.705      & 0.628      & 0.657    \\
\textsc{CMNN}        & 0.701      & 0.628      & 0.667    \\
\textsc{Skynet}    & 0.743      & 0.708      & 0.797    \\
\textsc{TPZ}       & 0.700      & 0.619      & 0.643    \\
\hline
\trainz	   & 0.699 		& 0.627 	& 0.666 \\
\end{tabular}
\end{table}
